---
title: "Summary for final report"
author: "Jackie Ouzman"
date: "08/09/2021"
output: html_document
---
```{r load library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(ggplot2)

library(formattable)
library(sf)
library(readxl)


library(gt)
library(glue)


library(rnaturalearth)


library(readr)

library(DT)
library(plotKML)
library(knitr)
library(png)


library(magick)


```

## Number of N and P trials for 2020 -2021  season 

CSIRO team have been supplied with spatial data for the location of strip trials.
Along with this information we have details on the type of trial (either N or P) and the fertilisers used.



Note that a few paddocks have both N and P trials.



Most paddocks have two zone, but some have just one and some have multiple zone.
This is filtering data out that is marked excluded from analysis and ensured I am only keeping unique Zone ID.

```{r zone shapefile 2020, message=TRUE, warning=FALSE, include=FALSE}
zone2020 <- st_read("W:/value_soil_testing_prj/Yield_data/2020/All_Zones_2020_wgs84.shp")


zone2020_df <- data.frame(zone2020)
zone2020_1 <- zone2020_df %>% dplyr::select(-geometry)


## some paddocks are excluded from the analysis
zone2020_df <- zone2020_1 %>% 
  filter(Status != "Excluded from Analysis")
#just keep a few clms
names(zone2020_df)
zone2020_df <- zone2020_df %>% 
  dplyr::select(Zone_ID,
                Strip_Type,
                Status,
                organisati,
                contact, 
                farmer,
                paddock)
rm(zone2020, zone2020_1)


zone2020_unique <- zone2020_df %>% 
  distinct(Zone_ID, Strip_Type, .keep_all = TRUE)

#how many zones with N / P strips?
zone2020_count <- zone2020_unique %>% 
  distinct(Zone_ID, .keep_all = TRUE) %>%
  group_by(Strip_Type) %>% 
  summarise(count_zones_by_type = n())



```

2020 season. Zone per fertilsier strip type (using zone shapefile).

```{r  numb strip trials, echo=FALSE, message=TRUE, warning=FALSE}

zone2020_count

```

2020 season.Paddocks per fertilsier strip type.

```{r zone 2020 per paddock, message=TRUE, warning=FALSE, include=FALSE}
#how many paddocks with N / P strips?

names(zone2020_unique)
#I cant just select paddock names beacuse some have the same name house and creek

zone_paddocks <- zone2020_unique %>%
  dplyr::mutate(paddock_farmer = paste0(paddock, "_", farmer)) %>% 
  dplyr::distinct(paddock_farmer, Strip_Type, .keep_all = TRUE)
  
zone_paddocks 
 
count_paddock <- zone_paddocks %>% 
  group_by(Strip_Type) %>% 
  summarise(count_paddocks_by_type = n())

```


```{r  numb paddocks, echo=FALSE, message=TRUE, warning=FALSE}

count_paddock


```


2020 season. How many growers?

```{r zone 2020 per farmers, message=TRUE, warning=FALSE, include=FALSE}

farmers_dist <- zone2020_unique %>% 
  dplyr::distinct(farmer,Strip_Type, .keep_all = TRUE)

farmers_count_type <- farmers_dist %>% 
    group_by(Strip_Type) %>% 
  summarise(count_farmers_by_type = n())

farmers_count <- farmers_dist %>% 
    summarise(count_farmers_by_type = n())



```

```{r number of farmers 2020, echo=FALSE, message=TRUE, warning=FALSE}
farmers_count
```


I can run the same analysis with the strip files but the numbers are slightly different because of the trials that have N and P.
So I will use the zone shapefile as a basis.
The code is here but I am not displaying the output.


```{r load_data1, message=TRUE, warning=FALSE, include=FALSE}

#note that this script runs off the shapefile and has on intermediate steps


spatial_data_no_yld <- st_read("W:/value_soil_testing_prj/Yield_data/2020/All_Strips_2020_wgs84.shp")

spatial <-  st_as_sf(spatial_data_no_yld, coords = c("X", "Y"), crs = 4326) #this is for map in later code chuck

spatial_data_no_yld_df <- data.frame(spatial_data_no_yld)
spatial_data_no_yld_df_1 <- spatial_data_no_yld_df %>% dplyr::select(-geometry)

## some paddocks are excluded from the analysis
spatial_data_no_yld_df <- spatial_data_no_yld_df_1 %>% 
   filter(Status != "Excluded from Analysis")

spatial_data_no_yld_df <- spatial_data_no_yld_df %>% 
  dplyr::mutate(ID_Rate_GSP_type = paste0(Paddock_ID, "-", Rate, "-", GSP,"-",Strip_Type ),
         ID_trial_type = paste0(Paddock_ID, "-",Strip_Type))

spatial_data_no_yld_df <-spatial_data_no_yld_df %>% 
  dplyr::mutate(Alt_GSP = ifelse(stringr::str_detect(GSP_list, "Alt GSP"), "Alt_GPS", "No_Alt_GSP"))

rm(spatial_data_no_yld_df_1)

strips_distinct_paddockID <- spatial_data_no_yld_df %>% 
  distinct(Paddock_ID, Strip_Type, .keep_all = TRUE)

```

```{r plot numb trials, message=TRUE, warning=FALSE, include=FALSE}
plot1 <-
  dplyr::distinct(strips_distinct_paddockID, Paddock_ID ,Strip_Type, .keep_all = TRUE) %>%
  dplyr::select(Paddock_ID, Strip_Type, Alt_GSP) %>%
  ggplot(aes(Strip_Type)) +
  geom_bar() +
  theme_bw() +
  geom_text(aes(y = ((..count..)), label = ((..count..))), stat = "count", vjust = -0.25) +
  labs(
    title = "Number of P and N trials. 2020 to 2021 season",
    y = "Count",
    x = "Type of trial",
    subtitle = paste0("Total number of paddocks = ", count(
      distinct(spatial_data_no_yld_df, ID_trial_type)
    ))
  )
plot1


```




## Number of N and P trials for 2019 -2020  season 

```{r zone shapefile 2019, message=TRUE, warning=FALSE, include=FALSE}
zone2019 <- st_read("W:/value_soil_testing_prj/Yield_data/finished/GIS_Results/All_Zones_2019_wgs84.shp")


zone2019_df <- data.frame(zone2019)
zone2019_1 <- zone2019_df %>% dplyr::select(-geometry)


## some paddocks are excluded from the analysis

#just keep a few clms

zone2019_df <- zone2019_1 %>% 
  dplyr::select(Zone_ID,
                Strip_Type, # I need to add this in ??
                #Status,
                organisati,
                contact, 
                farmer,
                paddock)
rm(zone2019, zone2019_1)


zone2019_df_unique <- zone2019_df %>% 
  distinct(Zone_ID, Strip_Type, .keep_all = TRUE)

#how many zones with N / P strips?
zone2019_count <- zone2019_df_unique %>% 
  distinct(Zone_ID, .keep_all = TRUE) %>%
  group_by(Strip_Type) %>% 
  summarise(count_zones_by_type = n())



```

2019 season. Zone per fertilsier strip type (using zone shapefile).

```{r  numb strip trials 2019, echo=FALSE, message=TRUE, warning=FALSE}

zone2019_count

```

2019 season.Paddocks per fertilsier strip type.

```{r zone 2019 per paddock, message=TRUE, warning=FALSE, include=FALSE}
#how many paddocks with N / P strips?


zone_paddocks2019 <- zone2019_df_unique %>%
  dplyr::mutate(paddock_farmer = paste0(paddock, "_", farmer)) %>% 
  dplyr::distinct(paddock_farmer, Strip_Type, .keep_all = TRUE)

paddocks2019 <-  zone_paddocks2019 %>% 
  group_by(Strip_Type) %>% 
  summarise(count_paddocks_by_type = n())


```


```{r  numb paddocks 2019, echo=FALSE, message=TRUE, warning=FALSE}

paddocks2019

```


2019 season. How many growers?

```{r zone 2019 per farmers, message=TRUE, warning=FALSE, include=FALSE}


farmers_dist2019 <- zone2019_df_unique %>% 
  dplyr::distinct(farmer,Strip_Type, .keep_all = TRUE)

farmers_count_type2019 <- farmers_dist2019 %>% 
  group_by(Strip_Type) %>% 
  summarise(count_farmers_by_type = n())

farmers_count2019 <- farmers_dist2019 %>% 
  summarise(count_farmers = n())



```

```{r number of farmers 2019, echo=FALSE, message=TRUE, warning=FALSE}

farmers_count_type2019
farmers_count2019
```

## How do the recommended rates 2020 -2021  season compare in the multiple zones in the paddock

I have used the low, medium, high rainfall class generated by the location of the trial.

Rather than using the database.
I have redone the N recommendation based on the revised rainfall class.

Sean is still getting back to me regarding how to calculate the P recommendation.
I assume it does not run off the rainfall class and I hope that the DB is correct.

I am using the DB for P recommended rates.



```{r stuff around getting recom rates just for our 2020 paddocks, message=TRUE, warning=FALSE, include=FALSE}


#########################################################################################################################################
## step 1 make a list of zone and a list of paddocks that will be included in the analysis 
#1b. zone codes
##########################################################################################################################################


zone2020 <- st_read("W:/value_soil_testing_prj/Yield_data/2020/All_Zones_2020_wgs84.shp")


zone2020_df <- data.frame(zone2020)
zone2020_1 <- zone2020_df %>% dplyr::select(-geometry)


## some paddocks are excluded from the analysis
zone2020_df <- zone2020_1 %>% 
  filter(Status != "Excluded from Analysis")
#just keep a few clms
names(zone2020_df)
zone2020_df <- zone2020_df %>% 
  dplyr::select(Zone_ID,
                Strip_Type,
                Status,
                organisati,
                contact, 
                farmer,
                paddock)
rm(zone2020, zone2020_1)


zone2020_unique <- zone2020_df %>% 
  distinct(Zone_ID, Strip_Type, .keep_all = TRUE)



rm(zone2020_df)

str(zone2020_unique)
zone2020_unique$length_zoneID <- nchar(zone2020_unique$Zone_ID)
zone2020_unique <- zone2020_unique %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))

list_of_paddocks_include <- unique(zone2020_unique$Paddock_ID)
list_of_zone_include <- (zone2020_unique$Zone_ID)
print(list_of_paddocks_include)
##########################################################################################################################################
# 2. Add rainfall data
##########################################################################################################################################

rainfall_fert <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_all_steps.csv")


rainfall_fert <- rainfall_fert %>%
  dplyr::select(
    Paddock_ID,
    #Rate,
    GSP	,
    #Strip_Rate,
    #organisati,
    #contact	,
    #farmer	,
    #paddock,
    #Strip_Type,
    av_rain,
    #Total_sum_N_content,
    #Total_sum_P_content,
    #Status
  )


##### filter out the data so I just have what I will use for the economic analysis


rainfall_fert <- rainfall_fert %>% 
  filter(Paddock_ID %in% list_of_paddocks_include)


### need to remove the Alt GPS from the rainfall data                
rainfall_fert <- rainfall_fert %>%   
  filter(is.na(GSP) | GSP == "GSP")


str(zone2020_unique) 
zone2020_unique$Paddock_ID <- as.double(zone2020_unique$Paddock_ID)
str(rainfall_fert)
rain_zone2020 <- left_join(zone2020_unique, rainfall_fert, by = "Paddock_ID")

# some seem to have come through twice ?? remove the

rain_zone2020 <- rain_zone2020 %>%
  filter(Status == "5. Report Complete" )

rain_zone2020 <- rain_zone2020 %>% dplyr::select(-GSP)
# beacuse I used the rainfall data file I have all the strip per zone -
#so I just need to keep unique values for zone ID and strip type

rain_zone2020 <- rain_zone2020 %>% 
  distinct(Zone_ID , Strip_Type, .keep_all = TRUE)

rain_zone2020 <- rain_zone2020 %>% 
  dplyr::mutate(
    rainfall_class = case_when(
      av_rain<=350 ~ "low",
      av_rain >500 ~ "high",
      TRUE ~ "medium"))


rm(rainfall_fert,zone2020_unique)

##########################################################################################################################################
#3b. add in the GRDC zones

zone2020_GRDC_bound <- st_read("W:/value_soil_testing_prj/Yield_data/2020/2020_GRDC_zones_test.shp")
zone2020_GRDC_bound <- zone2020_GRDC_bound %>% 
  dplyr::select(Zone_ID,
                # organisati,
                # contact,
                # farmer,
                # paddock,
                # Paddock_ID,
                # Strip_Type,
                AGROECOLOG)
zone2020_GRDC_bound <- as.data.frame(zone2020_GRDC_bound) %>% 
  dplyr::select(- geometry)
str(zone2020_GRDC_bound)
str(rain_zone2020)

rain_zone2020 <- left_join(rain_zone2020, zone2020_GRDC_bound)

##########################################################################################################################################
#4. Bring in Sean DB
##########################################################################################################################################

recom_rateDB <- read_excel( "W:/value_soil_testing_prj/Yield_data/2020/processing/GRDC 2020 Paddock Database_SA_VIC_May05 2021.xlsx")

# select only a few clms with recommedation 
recom_rateDB <- recom_rateDB %>% 
  dplyr::select(Zone_ID =    `Paddock code` ,
                Total_N = `Total N`, 
                p_rec =           `P rec`,
                n_rec_yld_low =   `N Rec (< 3 t/ha)` ,       
                n_rec_yld_med =   `N Rec (3-5 t/ha)` ,             
                n_rec_yld_high =  `N Rec (> 5 t/ha)`,
                SM_comment_Soil_N = `SM comment Soil N`,
                SM_comment_Soil_P = `SM comment Soil P`,
                SM_comment_Plant_Tissue = `SM comment Plant Tissue`
  ) 

recom_rateDB <-  dplyr::mutate(recom_rateDB,  maxN = apply(recom_rateDB[3:5], 1, max, na.rm = TRUE))



recom_rateDB$n_rec_yld_low <- as.double(recom_rateDB$n_rec_yld_low)
recom_rateDB$n_rec_yld_med <- as.double(recom_rateDB$n_rec_yld_med)
recom_rateDB$n_rec_yld_high <- as.double(recom_rateDB$n_rec_yld_high)




# remove redunant clm and replace inf
recom_rateDB <- recom_rateDB %>% 
  mutate(
    maxN = case_when(
      maxN >= 0 ~ maxN,
      TRUE ~ NA_real_
    )
  )
##make a paddock_ID clm
recom_rateDB$length_zoneID <- nchar(recom_rateDB$Zone_ID)
recom_rateDB <- recom_rateDB %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
recom_rateDB$Paddock_ID <- as.double(recom_rateDB$Paddock_ID)

str(recom_rateDB) #this has all the zones
str(rain_zone2020) #this has the paddock details
recom_rateDB$Zone_ID <- as.double(recom_rateDB$Zone_ID)


test <- left_join(rain_zone2020, recom_rateDB)




test$p_rec <- as.double(test$p_rec)



#############################################################################################################
### Redo the rec rates for N with my rainfall zone

test <- test %>% 
  mutate(Rec_N_jax = case_when(
    rainfall_class == "low" & Total_N <= 80 ~ ((80 -Total_N)/0.5),
    rainfall_class == "medium" & Total_N <= 160 ~ ((160 -Total_N)/0.5),
    rainfall_class == "high" & Total_N <= 240 ~ ((240 -Total_N)/0.5),
    TRUE                           ~ 0  ))









#just keep the data for the economic analysis
#now use this list to filter out my analysis...
test <- test %>% 
  filter(Zone_ID %in% list_of_zone_include)

test1 <- test %>%
  dplyr::select(
    "Zone_ID" ,
    "p_rec" ,
    "maxN" ,
    "Rec_N_jax", 
    "n_rec_yld_low",
    "n_rec_yld_med" ,
    "n_rec_yld_high",
    "SM_comment_Soil_N",
    "SM_comment_Soil_P",
    "SM_comment_Plant_Tissue",
    "Strip_Type",
    "Paddock_ID",
    "AGROECOLOG",
    "rainfall_class"
  )     


test1 <- test1 %>% 
  distinct(Zone_ID, .keep_all=TRUE)


zone_2020_step1 <- test1

rm(rain_zone2020, rainfall_fert, zone2020_unique, recom_rateDB,
   list_of_paddocks_include, list_of_zone_include, test, test1)



```


For P trials in 2020
The number of paddocks with either 1, 2,3 zones
How many paddocks have a P rec rate in zone 1 vs zone 2 that is higher than 5 kg


```{r rec rates different in zone 2020 P , echo=FALSE, message=TRUE, warning=FALSE}

rec_rate_2020_P <- zone_2020_step1 %>%  dplyr::filter(Strip_Type == "P Strip" | Strip_Type == "N Strip, P Strip")
Zone_In_Paddocks_P <- rec_rate_2020_P %>%  group_by(Paddock_ID) %>% 
  summarise(count_zone = n(),
            max_P_rec = max(p_rec, na.rm = FALSE),
            min_P_rec = min(p_rec, na.rm = FALSE))

Zone_In_Paddocks_P <- Zone_In_Paddocks_P %>% 
  mutate(diff_P_rec_rate = max_P_rec - min_P_rec)

Zone_In_Paddocks_P <- Zone_In_Paddocks_P %>% 
  mutate(count_of_diff = case_when(
    count_zone >1 & diff_P_rec_rate >5 ~ 1,
    TRUE ~ 0))
Zone_In_Paddocks_P %>%  group_by(count_zone) %>% 
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE))

Zone_In_Paddocks_P %>%  
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE),
            count =  n())



```

For N trials in 2020
The number of paddocks with either 1, 2,3 zones
How many paddocks have a P rec rate in zone 1 vs zone 2 that is higher than 10 kg

Note for the paddocks with the one than 2 zone I have just reported on the max difference.
For example what was the min and max recommedation.  


```{r rec rates different in zone 2020 N, echo=FALSE, message=TRUE, warning=FALSE}

#### is the recommedations different?  ###




zone_2020_step1$Strip_Type <- as.character(zone_2020_step1$Strip_Type)

rec_rate_2020_N <- zone_2020_step1 %>%  dplyr::filter(Strip_Type == "N Strip" | Strip_Type == "N Strip, P Strip" )


Zone_In_Paddocks_N <- rec_rate_2020_N %>%  group_by(Paddock_ID) %>% 
  summarise(count_zone = n(),
            max_N_rec = max(Rec_N_jax, na.rm = FALSE),
            min_N_rec = min(Rec_N_jax, na.rm = FALSE))

Zone_In_Paddocks_N <- Zone_In_Paddocks_N %>% 
  mutate(diff_N_rec_rate = max_N_rec - min_N_rec)

Zone_In_Paddocks_N <- Zone_In_Paddocks_N %>% 
  mutate(count_of_diff = case_when(
    count_zone >1 & diff_N_rec_rate >10 ~ 1,
    TRUE ~ 0))
Zone_In_Paddocks_N %>%  group_by(count_zone) %>% 
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE))

Zone_In_Paddocks_N %>%  
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE),
            count =  n())
```



## How do the recommended rates 2019 -2020  season compare in the multiple zones in the paddock
I have used Sean recommened rates but I think this is a problem beacuase the N rec rates run off rainfall zone 
Which I suspect is wrong.
Probably not a huge problem here because we are just comparing the results within the paddock which should have the same rainfall class.


```{r stuff around getting recom rates just for our 2019 paddocks, message=TRUE, warning=FALSE, include=FALSE}

################### 2019 data #######################################################
# ## How do the recommended rates 2020 -2021  season compare in the multiple zones in the paddock
# 
# I have used Sean recommended rates but I need to change this beacuse the rainfall class dont match the ecomonic work.
# 
#### SECTION for R markdown ####

# ```{r stuff around getting recom rates just for our 2020 paddocks, message=TRUE, warning=FALSE, include=FALSE}

#########################################################################################################################################
## step 1 make a list of zone and a list of paddocks that will be included in the analysis 
#1b. zone codes
##########################################################################################################################################


zone2019 <- st_read("W:/value_soil_testing_prj/Yield_data/finished/GIS_Results/All_Zones_2019_wgs84.shp")


zone2019_df <- data.frame(zone2019)
zone2019_1 <- zone2019_df %>% dplyr::select(-geometry)


## some paddocks are excluded from the analysis

#just keep a few clms

zone2019_df <- zone2019_1 %>% 
  dplyr::select(Zone_ID,
                Strip_Type, # I need to add this in ??
                #Status,
                organisati,
                contact, 
                farmer,
                paddock)
rm(zone2019, zone2019_1)


zone2019_df_unique <- zone2019_df %>% 
  distinct(Zone_ID, Strip_Type, .keep_all = TRUE)

#how many zones with N / P strips?
zone2019_count <- zone2019_df_unique %>% 
  distinct(Zone_ID, .keep_all = TRUE) %>%
  group_by(Strip_Type) %>% 
  summarise(count_zones_by_type = n())



str(zone2019_df_unique)
zone2019_df_unique$length_zoneID <- nchar(zone2019_df_unique$Zone_ID)
zone2019_df_unique <- zone2019_df_unique %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))

list_of_paddocks_include2019 <- unique(zone2019_df_unique$Paddock_ID)
list_of_zone_include_2019 <- (zone2019_df_unique$Zone_ID)

rm(zone2019_count, zone2019_df)

##########################################################################################################################################
# 2. Add rainfall data
##########################################################################################################################################
rainfall_fert_2019 <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_all_step_2019.csv")

#rainfall_fert <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_all_steps.csv")
names(rainfall_fert_2019)

rainfall_fert_2019 <- rainfall_fert_2019 %>%
  dplyr::select(
    Paddock_ID,
    #Rate,
    GSP	,
    #Strip_Rate,
    #organisati,
    #contact	,
    #farmer	,
    #paddock,
    #Strip_Type,
    av_rain,
    #Total_sum_N_content,
    #Total_sum_P_content,
    #Status
  )


##### filter out the data so I just have what I will use for the economic analysis


rainfall_fert_2019 <- rainfall_fert_2019 %>% 
  filter(Paddock_ID %in% list_of_paddocks_include2019)


### need to remove the Alt GPS from the rainfall data                
rainfall_fert_2019 <- rainfall_fert_2019 %>%   
  filter(is.na(GSP) | GSP == "GSP")



zone2019_df_unique$Paddock_ID <- as.double(zone2019_df_unique$Paddock_ID)

rain_zone2019 <- left_join(zone2019_df_unique, rainfall_fert_2019, by = "Paddock_ID")

# some seem to have come through twice ?? remove the

rain_zone2019 <- rain_zone2019 %>%
  distinct(Zone_ID, .keep_all = TRUE)

rain_zone2019 <- rain_zone2019 %>% dplyr::select(-GSP)
# beacuse I used the rainfall data file I have all the strip per zone -
#so I just need to keep unique values for zone ID and strip type

rain_zone2019 <- rain_zone2019 %>% 
  distinct(Zone_ID , Strip_Type, .keep_all = TRUE)

rain_zone2019 <- rain_zone2019 %>% 
  dplyr::mutate(
    rainfall_class = case_when(
      av_rain<=350 ~ "low",
      av_rain >500 ~ "high",
      TRUE ~ "medium"))


rm(rainfall_fert_2019,zone2019_df_unique)

##########################################################################################################################################
#3b. add in the GRDC zones

zone2019_GRDC_bound <- st_read("W:/value_soil_testing_prj/Yield_data/finished/GIS_Results/All_Zones_2019_GRDC_wgs84.shp")

zone2019_GRDC_bound <- zone2019_GRDC_bound %>% 
  dplyr::select(Zone_ID,
                # organisati,
                # contact,
                # farmer,
                # paddock,
                # Paddock_ID,
                # Strip_Type,
                AGROECOLOG)
zone2019_GRDC_bound <- as.data.frame(zone2019_GRDC_bound) %>% 
  dplyr::select(- geometry)
str(zone2019_GRDC_bound)
str(rain_zone2019)

rain_zone2019 <- left_join(rain_zone2019, zone2019_GRDC_bound)

##########################################################################################################################################
#4. Bring in Sean DB
##########################################################################################################################################

recom_rateDB2019 <- read_excel( "W:/value_soil_testing_prj/data_base/downloaded_sep2021/GRDC 2019 Paddock Database_SA_VIC_June11 2021.xlsx")

# select only a few clms with recommedation 
recom_rateDB2019 <- recom_rateDB2019 %>% 
  dplyr::select(Zone_ID =    `Paddock code` ,
                Total_N = `Total N`, 
                p_rec =           `P rec`,
                n_rec_yld_low =   `N Rec (< 3 t/ha)` ,       
                n_rec_yld_med =   `N Rec (3-5 t/ha)` ,             
                n_rec_yld_high =  `N Rec (> 5 t/ha)`)
                # SM_comment_Soil_N = `SM comment Soil N`,
                # SM_comment_Soil_P = `SM comment Soil P`,
                # SM_comment_Plant_Tissue = `SM comment Plant Tissue`
  

recom_rateDB2019 <-  dplyr::mutate(recom_rateDB2019,  
                                   maxN = apply(recom_rateDB2019[4:6], 1, max, na.rm = TRUE))



recom_rateDB2019$n_rec_yld_low <- as.double(recom_rateDB2019$n_rec_yld_low)
recom_rateDB2019$n_rec_yld_med <- as.double(recom_rateDB2019$n_rec_yld_med)
recom_rateDB2019$n_rec_yld_high <- as.double(recom_rateDB2019$n_rec_yld_high)




# remove redunant clm and replace inf
recom_rateDB2019 <- recom_rateDB2019 %>% 
  mutate(
    maxN = case_when(
      maxN >= 0 ~ maxN,
      TRUE ~ NA_real_
    )
  )
##make a paddock_ID clm
recom_rateDB2019$length_zoneID <- nchar(recom_rateDB2019$Zone_ID)
recom_rateDB2019 <- recom_rateDB2019 %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
recom_rateDB2019$Paddock_ID <- as.double(recom_rateDB2019$Paddock_ID)

str(recom_rateDB2019) #this has all the zones
str(rain_zone2019) #this has the paddock details
recom_rateDB2019$Zone_ID <- as.double(recom_rateDB2019$Zone_ID)


test <- left_join(rain_zone2019, recom_rateDB2019)




test$p_rec <- as.double(test$p_rec)



#############################################################################################################
### Redo the rec rates for N with my rainfall zone

test <- test %>% 
  mutate(Rec_N_jax = case_when(
    rainfall_class == "low" & Total_N <= 80 ~ ((80 -Total_N)/0.5),
    rainfall_class == "medium" & Total_N <= 160 ~ ((160 -Total_N)/0.5),
    rainfall_class == "high" & Total_N <= 240 ~ ((240 -Total_N)/0.5),
    TRUE                           ~ 0  ))









#just keep the data for the economic analysis
#now use this list to filter out my analysis...
test <- test %>% 
  filter(Zone_ID %in% list_of_zone_include_2019)

test1 <- test %>%
  dplyr::select(
    "Zone_ID" ,
    "p_rec" ,
    "maxN" ,
    "Rec_N_jax", 
    "n_rec_yld_low",
    "n_rec_yld_med" ,
    "n_rec_yld_high",
    # "SM_comment_Soil_N",
    # "SM_comment_Soil_P",
    # "SM_comment_Plant_Tissue",
    "Strip_Type",
    "Paddock_ID",
    "AGROECOLOG",
    "rainfall_class"
  )     


## make sure I have only one zone ID

test1 <- test1 %>% 
  distinct(Zone_ID, .keep_all=TRUE)


zone_2019_step1 <- test1 

rm(rain_zone2019, recom_rateDB2019, test, test1, zone2019_GRDC_bound,
   list_of_paddocks_include2019, list_of_zone_include_2019)

zone_2019_step1 %>% group_by(Strip_Type) %>% 
  summarise(count= n())

names(zone_2019_step1)

```


For N trials in 2019
The number of paddocks with either 1, 2,3 zones
How many paddocks have a P rec rate in zone 1 vs zone 2 that is higher than 10 kg


```{r rec rates different in zone 2019 N , echo=FALSE, message=TRUE, warning=FALSE}

zone_2019_step1$Strip_Type <- as.character(zone_2019_step1$Strip_Type)

rec_rate_2019_N <- zone_2019_step1 %>%  dplyr::filter(Strip_Type == "N Strip" | Strip_Type == "N Strip, P Strip" )

Zone_In_Paddocks_N <- rec_rate_2019_N %>%  group_by(Paddock_ID) %>% 
  summarise(count_zone = n(),
            max_N_rec = max(Rec_N_jax, na.rm = FALSE),
            min_N_rec = min(Rec_N_jax, na.rm = FALSE))

Zone_In_Paddocks_N <- Zone_In_Paddocks_N %>% 
  mutate(diff_N_rec_rate = max_N_rec - min_N_rec)

Zone_In_Paddocks_N <- Zone_In_Paddocks_N %>% 
  mutate(count_of_diff = case_when(
    count_zone >1 & diff_N_rec_rate >10 ~ 1,
    TRUE ~ 0))
Zone_In_Paddocks_N %>%  group_by(count_zone) %>% 
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE))

Zone_In_Paddocks_N %>%  
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE),
            count =  n())




```

For P trials in 2019
The number of paddocks with either 1, 2,3 zones
How many paddocks have a P rec rate in zone 1 vs zone 2 that is higher than 5 kg


```{r rec rates different in zone 2019 P , echo=FALSE, message=TRUE, warning=FALSE}
#### is the recommedations different?  ###
rec_rate_2019_P <- zone_2019_step1 %>%  dplyr::filter(Strip_Type == "P Strip" | Strip_Type == "N Strip, P Strip")
Zone_In_Paddocks_P <- rec_rate_2019_P %>%  group_by(Paddock_ID) %>% 
  summarise(count_zone = n(),
            max_P_rec = max(p_rec, na.rm = FALSE),
            min_P_rec = min(p_rec, na.rm = FALSE))

Zone_In_Paddocks_P <- Zone_In_Paddocks_P %>% 
  mutate(diff_P_rec_rate = max_P_rec - min_P_rec)

Zone_In_Paddocks_P <- Zone_In_Paddocks_P %>% 
  mutate(count_of_diff = case_when(
    count_zone >1 & diff_P_rec_rate >5 ~ 1,
    TRUE ~ 0))
Zone_In_Paddocks_P %>%  group_by(count_zone) %>% 
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE))

Zone_In_Paddocks_P %>%  
  summarise(sum_of_when_diff = sum(count_of_diff, na.rm = TRUE),
            count =  n())

```



## Details on the soil test, recommend rates and the average GSP

### 2019 data 

This dataset is not great.
I have patchy records for the fertiliser applied and how much was applied over the season.

Therese has done a lot of work here but some sites just don't seem to add up.
A variety of problems, I have used her work as a cross refrence.

Sean has used the rainfall zone in the database to assign the N recommended rates.
This is a problem beacuse if I use the location of the sites and BOM average grid,
I get a differnt rainfall class.

I have done the N rec rates again.



```{r stuff around recom rates just for our 2019 paddocks vs GSP, message=TRUE, warning=FALSE, include=FALSE}

###### 2019 #######
### The data for recom rates vs GSP ######



### Get rainfall for sites
#1.bring in shapefile strip data


all_strips2019 <- st_read("W:/value_soil_testing_prj/Yield_data/finished/GIS_Results/All_Strips_2019_wgs84.shp")
str(all_strips2019)
all_strips2019 <- all_strips2019 %>%
  dplyr::select(Paddock_ID, geometry) 

#2.turn polygons into points - centriod

all_strips2019_centroid = st_centroid(all_strips2019)
all_strips2019_centroid <- all_strips2019_centroid %>%  filter(!is.na(Paddock_ID))
###################################################################################################
###################  rainfall data from BOM ########################################################
####################################################################################################

# downloaded gridded rainfall data from BOM

#http://www.bom.gov.au/jsp/ncc/climate_averages/rainfall/index.jsp
#choosing the average rainfall - convert the text file into a grid and extract the gridded values to points

av_rain <- raster::raster("W:/value_soil_testing_prj/Yield_data/2020/processing/rain_grid")
av_rain

##2. extract strips coordinates points from the raster (eg shapefile points and average rainfall grid)
all_strips2019_centroid$av_rain <- raster::extract(av_rain, all_strips2019_centroid)
all_strips2019_centroid
all_strips2019_centroid_df <- as.data.frame(all_strips2019_centroid ) %>%  dplyr::select(-geometry)
str(all_strips2019_centroid_df)

rm(all_strips2019, all_strips2019_centroid, av_rain)

rain_2019 <- all_strips2019_centroid_df %>% 
  dplyr::mutate(
    rainfall_class = case_when(
      av_rain<=350 ~ "low",
      av_rain >500 ~ "high",
      TRUE ~ "medium"))
rain_2019 <- rain_2019 %>%  distinct(Paddock_ID, .keep_all = TRUE)
rm(all_strips2019_centroid_df)

####################################################################################################################

fertiliser_applied2019 <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_all_step_2019.csv")
str(fertiliser_applied2019)

fert_2019 <- fertiliser_applied2019 %>% 
  dplyr::select(Paddock_ID, Rate,GSP,
                Strip_Rate , Strip_Type,
                organisati,
                contact,
                farmer,
                join_field,
                Total_sum_N_content,
                Total_sum_P_content) 

### add in the rainfall
fert_2019_rain <- left_join(fert_2019, rain_2019)
rm(fert_2019, fertiliser_applied2019, rain_2019)
str(fert_2019_rain)

#Using the fert rates I can pull out the GSP paddock code and strip type
fert_2019_rain_GSP <- fert_2019_rain %>%  filter(!is.na( GSP))
str(fert_2019_rain_GSP)
fert_2019_rain_GSP <- fert_2019_rain_GSP %>% dplyr::select(Paddock_ID,
                                                       Strip_Type,
                                                       Total_sum_N_content,
                                                       Total_sum_P_content,
                                                       av_rain,
                                                       rainfall_class)
rm(fert_2019_rain)
####################################################################################################################
## bring in rec rates ##

recom_rateDB2019 <- read_excel( "W:/value_soil_testing_prj/data_base/downloaded_sep2021/GRDC 2019 Paddock Database_SA_VIC_June11 2021.xlsx")
str(recom_rateDB2019)
# select only a few clms with recommedation 
recom_rateDB2019 <- recom_rateDB2019 %>% 
  dplyr::select(Zone_ID =    `Paddock code` ,
                Total_N = `Total N`, 
                p_rec =           `P rec`,
                n_rec_yld_low =   `N Rec (< 3 t/ha)` ,       
                n_rec_yld_med =   `N Rec (3-5 t/ha)` ,             
                n_rec_yld_high =  `N Rec (> 5 t/ha)`,
                Colwell,
                DGT,
                PBI
                #SM_comment_Soil_N = `SM comment Soil N`,
                #SM_comment_Soil_P = `SM comment Soil P`,
                #SM_comment_Plant_Tissue = `SM comment Plant Tissue`
  ) 

recom_rateDB2019$n_rec_yld_low <- as.double(recom_rateDB2019$n_rec_yld_low)
recom_rateDB2019$n_rec_yld_med <- as.double(recom_rateDB2019$n_rec_yld_med)
recom_rateDB2019$n_rec_yld_high <- as.double(recom_rateDB2019$n_rec_yld_high)
recom_rateDB2019$Colwell <- as.double(recom_rateDB2019$Colwell)
recom_rateDB2019$DGT <- as.double(recom_rateDB2019$DGT)
recom_rateDB2019$PBI <- as.double(recom_rateDB2019$PBI)

recom_rateDB2019 <-  dplyr::mutate(recom_rateDB2019,  maxN = apply(recom_rateDB2019[4:6], 1, max, na.rm = TRUE))


# remove redunant clm and replace inf
recom_rateDB2019 <- recom_rateDB2019 %>% 
  mutate(
    maxN = case_when(
      maxN >= 0 ~ maxN,
      TRUE ~ NA_real_
    )
  )

recom_rateDB2019 <- recom_rateDB2019 %>% 
  dplyr::select(Zone_ID  ,
                p_rec ,
                maxN,
                Total_N,
                Colwell,
                DGT,
                PBI)

##make a paddock_ID clm
recom_rateDB2019$length_zoneID <- nchar(recom_rateDB2019$Zone_ID)
recom_rateDB2019 <- recom_rateDB2019 %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
recom_rateDB2019$Paddock_ID <- as.double(recom_rateDB2019$Paddock_ID)

str(recom_rateDB2019) #this has all the zones
str(fert_2019_rain_GSP) #this has the paddock details

zone_rec_rate_GSP_2019 <- left_join(recom_rateDB2019, fert_2019_rain_GSP)
#if it has no rainfall class we didnt have strip info so chuck it!
zone_rec_rate_GSP_2019 <- zone_rec_rate_GSP_2019 %>% 
  filter(!is.na(rainfall_class))

rm(fert_2019_rain_GSP, recom_rateDB2019)
zone_rec_rate_GSP_2019$Strip_Type <- as.character(zone_rec_rate_GSP_2019$Strip_Type)
zone_rec_rate_GSP_2019$p_rec <- as.double(zone_rec_rate_GSP_2019$p_rec)

str(zone_rec_rate_GSP_2019)

#############################################################################################################
### Redo the rec rates for N with my rainfall zone

zone_rec_rate_GSP_2019 <- zone_rec_rate_GSP_2019 %>% 
  mutate(Rec_N_jax = case_when(
    rainfall_class == "low" & Total_N <= 80 ~ ((80 -Total_N)/0.5),
    rainfall_class == "medium" & Total_N <= 160 ~ ((160 -Total_N)/0.5),
    rainfall_class == "high" & Total_N <= 240 ~ ((240 -Total_N)/0.5),
    TRUE                           ~ 0  ))

str(zone_rec_rate_GSP_2019)



```

```{r rec rates vs GSP 2019 N , echo=FALSE, message=TRUE, warning=FALSE}

#############################################################################################################


            
            
zone_rec_rate_GSP_2019_N <- zone_rec_rate_GSP_2019 %>%  dplyr::filter(Strip_Type == "N Strip")
zone_rec_rate_GSP_2019_N_low <- zone_rec_rate_GSP_2019_N %>%  dplyr::filter(rainfall_class == "low")
zone_rec_rate_GSP_2019_N_high <- zone_rec_rate_GSP_2019_N %>%  dplyr::filter(rainfall_class == "high")


zone_rec_rate_GSP_2019_N %>%  group_by(rainfall_class) %>%
  summarise(Av_N_soil = mean(Total_N, na.rm = TRUE),
           
            Av_N_rec_rate = mean(Rec_N_jax, na.rm = TRUE),
            #median_N_rec_rate = median(Rec_N_jax, na.rm = TRUE),
            
            Av_N_GSP = mean(Total_sum_N_content, na.rm = TRUE),
            #median_N_GSP = median(Total_sum_N_content, na.rm = TRUE)
            ) %>% 
  arrange(rainfall_class)

zone_rec_rate_GSP_2019_P <- zone_rec_rate_GSP_2019 %>%  dplyr::filter(Strip_Type == "P Strip")
zone_rec_rate_GSP_2019_P %>%  group_by(rainfall_class) %>%
  summarise(Av_P_Colwell = mean(Colwell, na.rm = TRUE),
            Av_P_DGT = mean(DGT, na.rm = TRUE),
            Av_P_PBI = mean(PBI, na.rm = TRUE),
            
            Av_P_rec_rate = mean(p_rec, na.rm = TRUE),
            #median_N_rec_rate = median(Rec_N_jax, na.rm = TRUE),
            
            Av_P_GSP = mean(Total_sum_P_content, na.rm = TRUE),
            #median_N_GSP = median(Total_sum_P_content, na.rm = TRUE)
  ) %>% 
  arrange(rainfall_class)
```

### 2020 data

```{r stuff around recom rates just for our 2020 paddocks vs GSP, message=TRUE, warning=FALSE, include=FALSE}

###### 2020 #######
### The data for recom rates vs GSP ######



### Get rainfall for sites
#1.bring in shapefile strip data


all_strips2020 <- st_read("W:/value_soil_testing_prj/Yield_data/2020/All_Strips_2020_wgs84.shp")
str(all_strips2020)
all_strips2020 <- all_strips2020 %>%
  dplyr::select(Paddock_ID, geometry) 

#2.turn polygons into points - centriod

all_strips20202_centroid = st_centroid(all_strips2020)
all_strips20202_centroid <- all_strips20202_centroid %>%  filter(!is.na(Paddock_ID))
###################################################################################################
###################  rainfall data from BOM ########################################################
####################################################################################################

# downloaded gridded rainfall data from BOM

#http://www.bom.gov.au/jsp/ncc/climate_averages/rainfall/index.jsp
#choosing the average rainfall - convert the text file into a grid and extract the gridded values to points

av_rain <- raster::raster("W:/value_soil_testing_prj/Yield_data/2020/processing/rain_grid")
av_rain

##2. extract strips coordinates points from the raster (eg shapefile points and average rainfall grid)
all_strips20202_centroid$av_rain <- raster::extract(av_rain, all_strips20202_centroid)
all_strips20202_centroid
all_strips20202_centroid_df <- as.data.frame(all_strips20202_centroid ) %>%  dplyr::select(-geometry)
str(all_strips20202_centroid_df)

rm(all_strips2020, all_strips20202_centroid, av_rain)

rain_2019 <- all_strips20202_centroid_df %>% 
  dplyr::mutate(
    rainfall_class = case_when(
      av_rain<=350 ~ "low",
      av_rain >500 ~ "high",
      TRUE ~ "medium"))
rain_2020 <- rain_2019 %>%  distinct(Paddock_ID, .keep_all = TRUE)
rm(all_strips20202_centroid_df)

####################################################################################################################

fertiliser_applied2020 <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_all_steps.csv")
str(fertiliser_applied2020)

fert_2020 <- fertiliser_applied2020 %>% 
  dplyr::select(Paddock_ID, Rate,GSP,
                Strip_Rate , Strip_Type,
                organisati,
                contact,
                farmer,
                join_field,
                Total_sum_N_content,
                Total_sum_P_content) 

### add in the rainfall
fert_2020_rain <- left_join(fert_2020, rain_2020)
rm(fert_2020, fertiliser_applied2020, rain_2020)
str(fert_2020_rain)

#Using the fert rates I can pull out the GSP paddock code and strip type
fert_2020_rain_GSP <- fert_2020_rain %>%  filter(!is.na( GSP))
str(fert_2020_rain_GSP)
fert_2020_rain_GSP <- fert_2020_rain_GSP %>% dplyr::select(Paddock_ID,
                                                       Strip_Type,
                                                       Total_sum_N_content,
                                                       Total_sum_P_content,
                                                       av_rain,
                                                       rainfall_class)
rm(fert_2020_rain)
####################################################################################################################
## bring in rec rates ##

recom_rateDB2020 <- read_excel( "W:/value_soil_testing_prj/data_base/downloaded_sep2021/GRDC 2020 Paddock Database_SA_VIC_June11 2021.xlsx")
str(recom_rateDB2020)
# select only a few clms with recommedation 
recom_rateDB2020 <- recom_rateDB2020 %>% 
  dplyr::select(Zone_ID =    `Paddock code` ,
                Total_N = `Total N`, 
                p_rec =           `P rec`,
                n_rec_yld_low =   `N Rec (< 3 t/ha)` ,       
                n_rec_yld_med =   `N Rec (3-5 t/ha)` ,             
                n_rec_yld_high =  `N Rec (> 5 t/ha)`,
                Colwell,
                DGT,
                PBI
                #SM_comment_Soil_N = `SM comment Soil N`,
                #SM_comment_Soil_P = `SM comment Soil P`,
                #SM_comment_Plant_Tissue = `SM comment Plant Tissue`
  ) 


recom_rateDB2020$n_rec_yld_low <- as.double(recom_rateDB2020$n_rec_yld_low)
recom_rateDB2020$n_rec_yld_med <- as.double(recom_rateDB2020$n_rec_yld_med)
recom_rateDB2020$n_rec_yld_high <- as.double(recom_rateDB2020$n_rec_yld_high)
recom_rateDB2020$Colwell <- as.double(recom_rateDB2020$Colwell)
recom_rateDB2020$DGT <- as.double(recom_rateDB2020$DGT)

str(recom_rateDB2020)
recom_rateDB2020 <-  dplyr::mutate(recom_rateDB2020,  maxN = apply(recom_rateDB2020[4:6], 1, max, na.rm = TRUE))


# remove redunant clm and replace inf
recom_rateDB2020 <- recom_rateDB2020 %>% 
  mutate(
    maxN = case_when(
      maxN >= 0 ~ maxN,
      TRUE ~ NA_real_
    )
  )

recom_rateDB2020 <- recom_rateDB2020 %>% 
  dplyr::select(Zone_ID  ,
                p_rec ,
                maxN,
                Total_N,
                Colwell,
                DGT,
                PBI)

##make a paddock_ID clm
recom_rateDB2020$length_zoneID <- nchar(recom_rateDB2020$Zone_ID)
recom_rateDB2020 <- recom_rateDB2020 %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
recom_rateDB2020$Paddock_ID <- as.double(recom_rateDB2020$Paddock_ID)

str(recom_rateDB2020) #this has all the zones
str(fert_2020_rain_GSP) #this has the paddock details

zone_rec_rate_GSP_2020 <- left_join(recom_rateDB2020, fert_2020_rain_GSP)
#if it has no rainfall class we didnt have strip info so chuck it!
zone_rec_rate_GSP_2020 <- zone_rec_rate_GSP_2020 %>% 
  filter(!is.na(rainfall_class))

rm(fert_2020_rain_GSP, recom_rateDB2020)
zone_rec_rate_GSP_2020$Strip_Type <- as.character(zone_rec_rate_GSP_2020$Strip_Type)
zone_rec_rate_GSP_2020$p_rec <- as.double(zone_rec_rate_GSP_2020$p_rec)

#str(zone_rec_rate_GSP_2019)

#############################################################################################################
### Redo the rec rates for N with my rainfall zone

zone_rec_rate_GSP_2020 <- zone_rec_rate_GSP_2020 %>% 
  mutate(Rec_N_jax = case_when(
    rainfall_class == "low" & Total_N <= 80 ~ ((80 -Total_N)/0.5),
    rainfall_class == "medium" & Total_N <= 160 ~ ((160 -Total_N)/0.5),
    rainfall_class == "high" & Total_N <= 240 ~ ((240 -Total_N)/0.5),
    TRUE                           ~ 0  ))


str(zone_rec_rate_GSP_2020)


```

```{r rec rates vs GSP 2020 N , echo=FALSE, message=TRUE, warning=FALSE}
#############################################################################################################


zone_rec_rate_GSP_2020_N <- zone_rec_rate_GSP_2020 %>%  dplyr::filter(Strip_Type == "N Strip")
zone_rec_rate_GSP_2020_N_low <- zone_rec_rate_GSP_2020_N %>%  dplyr::filter(rainfall_class == "low")
zone_rec_rate_GSP_2020_N_high <- zone_rec_rate_GSP_2020_N %>%  dplyr::filter(rainfall_class == "high")


zone_rec_rate_GSP_2020_N %>%  group_by(rainfall_class) %>%
  summarise(Av_N_soil = mean(Total_N, na.rm = TRUE),
           
            Av_N_rec_rate = mean(Rec_N_jax, na.rm = TRUE),
            #median_N_rec_rate = median(Rec_N_jax, na.rm = TRUE),
            
            Av_N_GSP = mean(Total_sum_N_content, na.rm = TRUE),
            #median_N_GSP = median(Total_sum_N_content, na.rm = TRUE)
            ) %>% 
  arrange(rainfall_class)

# zone_rec_rate_GSP_2020_N %>%  group_by(rainfall_class) %>%
#   summarise(Av_N_soil = mean(Total_N, na.rm = TRUE),
#             Av_N_rec_rate = mean(maxN, na.rm = TRUE),
#             Av_N_GSP = mean(Total_sum_N_content, na.rm = TRUE),
#             ) %>% 
#   arrange(rainfall_class)

zone_rec_rate_GSP_2020_P <- zone_rec_rate_GSP_2020 %>%  dplyr::filter(Strip_Type == "P Strip")

zone_rec_rate_GSP_2020_P %>%  group_by(rainfall_class) %>%
  summarise(Av_P_Colwell = mean(Colwell, na.rm = TRUE),
            Av_P_DGT = mean(DGT, na.rm = TRUE),
            Av_P_PBI = mean(PBI, na.rm = TRUE),
            
            Av_P_rec_rate = mean(p_rec, na.rm = TRUE),
            #median_N_rec_rate = median(Rec_N_jax, na.rm = TRUE),
            
            Av_P_GSP = mean(Total_sum_P_content, na.rm = TRUE),
            #median_N_GSP = median(Total_sum_P_content, na.rm = TRUE)
  ) %>% 
  arrange(rainfall_class)
```




The yield difference for the 2019.
Oh boy this data is a mess - have stared here and there - multiple changes.
The first bit of code is just getting the dataset ready.

(if you need to unpack it more scrap_notes4_2019 script is good to use)



```{r stuff around yield respose for 2019 paddocks vs GSP, message=TRUE, warning=FALSE, include=FALSE}




## getting the yield difference and GM difference between GSP and Approx
all_strips2019 <- st_read("W:/value_soil_testing_prj/Yield_data/finished/GIS_Results/All_Strips_2019_wgs84.shp")
all_strips2019 <- all_strips2019 %>%
  dplyr::select(Paddock_ID, geometry) 

#2.turn polygons into points - centriod
all_strips2019_centroid = st_centroid(all_strips2019)
all_strips2019_centroid <- all_strips2019_centroid %>%  filter(!is.na(Paddock_ID))
#3.
av_rain <- raster::raster("W:/value_soil_testing_prj/Yield_data/2020/processing/rain_grid")

##3a. extract strips coordinates points from the raster (eg shapefile points and average rainfall grid)
all_strips2019_centroid$av_rain <- raster::extract(av_rain, all_strips2019_centroid)
all_strips2019_centroid_df <- as.data.frame(all_strips2019_centroid ) %>%  dplyr::select(-geometry)
rm(all_strips2019, all_strips2019_centroid, av_rain)


## add in GRDC zone
zone2019_GRDC_bound <- st_read("W:/value_soil_testing_prj/Yield_data/finished/GIS_Results/All_Zones_2019_GRDC_wgs84.shp")

zone2019_GRDC_bound <- zone2019_GRDC_bound %>% 
  dplyr::select(Zone_ID,
                AGROECOLOG)
zone2019_GRDC_bound <- as.data.frame(zone2019_GRDC_bound) %>% 
  dplyr::select(- geometry)
##make a paddock_ID clm
zone2019_GRDC_bound$length_zoneID <- nchar(zone2019_GRDC_bound$Zone_ID)
zone2019_GRDC_bound <- zone2019_GRDC_bound %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
zone2019_GRDC_bound$Paddock_ID <- as.double(zone2019_GRDC_bound$Paddock_ID)

str(zone2019_GRDC_bound)
str(all_strips2019_centroid_df)

all_strips2019_centroid_df <- left_join(all_strips2019_centroid_df, zone2019_GRDC_bound)
all_strips2019_centroid_df <- all_strips2019_centroid_df %>% 
  dplyr::mutate(
    rainfall_class = case_when(
      av_rain<=350 ~ "low",
      av_rain >500 ~ "high",
      TRUE ~ "medium"))


all_strips2019_centroid_df <- all_strips2019_centroid_df %>% 
  dplyr::select( Paddock_ID, 
                AGROECOLOG, 
                rainfall_class) 
                
### oops I need the rates from the fert df

fertiliser_applied2019 <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_all_step_2019.csv")
str(fertiliser_applied2019)

fert_2019 <- fertiliser_applied2019 %>% 
  dplyr::select(Paddock_ID, Rate,GSP,Strip_Type,
                Total_sum_N_content,
                Total_sum_P_content) 

rm(fertiliser_applied2019, zone2019_GRDC_bound)
str(all_strips2019_centroid_df)
str(fert_2019)
## add it to the other data

details_2019 <- left_join(fert_2019, all_strips2019_centroid_df)
rm(fert_2019,all_strips2019_centroid_df )

names(details_2019)

## The GSP is coded a bit strange its either a GPS or number - should all be GSP
details_2019 <- details_2019 %>% 
  dplyr::mutate(GSP = case_when(
    GSP =!is.na(GSP) ~ "GSP" 
  ))
str(details_2019)
## remove a couple of problem strips
details_2019 <- details_2019 %>% 
  filter(Paddock_ID != 31712  |  !is.na(Rate))
details_2019 <- details_2019 %>% 
  filter(Paddock_ID != 51521  |  !is.na(Rate))
details_2019 <- details_2019 %>% 
  filter(Paddock_ID != 51522  |  !is.na(Rate))

#######################################################################################

## bring in the t.test data results

set1_2019 <- read.csv("W:/value_soil_testing_prj/Yield_data/finished/complied/use/Landmark_with_soil2020-06-24_For_TM.csv")
set2_2019 <- read.csv("W:/value_soil_testing_prj/Yield_data/finished/complied/use/Non_landmark_results_soil_and_pair_rates2020-06-25_For_TM.csv")
str(set1_2019)
names(set1_2019)
set1_2019 <- set1_2019 %>% 
  dplyr::select(Zone_ID = Paddock.code,
                Organisation,
                Contact,
                Farmer,
                Paddock_tested,
                Rates,
                Yld,
                P_value,Mean_diff,rounded,Significant)

str(set2_2019)
names(set2_2019)

set2_2019 <- set2_2019 %>% 
  dplyr::select(Zone_ID = Paddock.code,
                Organisation,
                Contact,
                Farmer,
                Paddock_tested,
                Rates,
                Yld,
                P_value,Mean_diff,rounded,Significant)
# Pole has rates in shapefile that are different to this, its that same but expressed in different units

set2_2019 <- set2_2019 %>%
  dplyr::mutate(Rates = case_when(
    Paddock_tested == 	"Georges" & Rates ==  0 ~ 0,
    Paddock_tested == 	"Georges" & Rates ==  3 ~ 23,
    Paddock_tested == 	"Georges" & Rates ==  6 ~ 46,
    Paddock_tested == 	"Georges" & Rates ==  9 ~ 69,
    Paddock_tested == 	"Georges" & Rates ==  12 ~ 92,
    Paddock_tested == 	"Georges" & Rates ==  15 ~ 115,
    TRUE ~ as.double(Rates)
  ))

t.test_2019 <- rbind(set2_2019, set1_2019)
rm(set1_2019, set2_2019)

##make a paddock_ID clm
t.test_2019$length_zoneID <- nchar(t.test_2019$Zone_ID)
t.test_2019 <- t.test_2019 %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
t.test_2019$Paddock_ID <- as.double(t.test_2019$Paddock_ID)



## The t test data does not have N or P Strips and there is duplication
str(t.test_2019)
t.test_2019 <- t.test_2019 %>% 
  dplyr::mutate(Strip_Type = case_when(
    Paddock_ID == 31132 ~ "N Strip",
    Paddock_ID == 31231 ~ "N Strip",
    Paddock_ID == 31233 ~ "N Strip",
    Paddock_ID == 31711 ~ "N Strip",
    Paddock_ID == 31712 ~ "N Strip",
    Paddock_ID == 31726 ~ "N Strip",
    Paddock_ID == 51512 ~ "N Strip",
    Paddock_ID == 51713 ~ "N Strip",
    Paddock_ID == 51911 ~ "N Strip",
    Paddock_ID == 51914 ~ "N Strip",
    Paddock_ID == 51915 ~ "N Strip",
    Paddock_ID == 52413 ~ "N Strip",
    Paddock_ID == 52444 ~ "N Strip",
    Paddock_ID == 52453 ~ "N Strip",
    Paddock_ID == 51511 ~ "N Strip",
    Paddock_ID == 33311 ~ "N and P Strip",
    Paddock_ID == 33321 ~ "N and P Strip",
    Paddock_ID == 33331 ~ "N and P Strip",
    TRUE ~ "P Strip"
  ))
## Ann paddocks are a bit of a mess some results are for P and some are for N I have used TB analysis to work out which is which
t.test_2019 <- t.test_2019 %>% 
  dplyr::mutate(Strip_Type = case_when(
    #Schlitz_M2
    Zone_ID == 333110 & Rates == 0 & Yld < 3 ~ "N Strip",
    Zone_ID == 333110 & Rates == 60  ~ "N Strip",
    Zone_ID == 333110 & Rates == 120  ~ "N Strip",
    
    Zone_ID == 333110 & Rates == 0 & Yld > 3 ~ "P Strip",
    Zone_ID == 333110 & Rates == 20  ~ "P Strip",
    Zone_ID == 333110 & Rates == 40  ~ "P Strip",
    Zone_ID == 333110 & Rates == 80  ~ "P Strip",
    
    
    #Schlitz_M2
    Zone_ID == 333111 & Rates == 0 & Yld > 2.69 ~ "N Strip",
    Zone_ID == 333111 & Rates == 60  ~ "N Strip",
    Zone_ID == 333111 & Rates == 120  ~ "N Strip",
    
    Zone_ID == 333111 & Rates == 0 & Yld < 2.69 ~ "P Strip",
    Zone_ID == 333111 & Rates == 20  ~ "P Strip",
    Zone_ID == 333111 & Rates == 40  ~ "P Strip",
    Zone_ID == 333111 & Rates == 80  ~ "P Strip",
    
    #Chamberlain_2
    Zone_ID == 333211 & Rates == 25  ~ "P Strip",
    Zone_ID == 333211 & Rates == 50  ~ "P Strip",
    Zone_ID == 333211 & Rates == 75  ~ "P Strip",
    
    Zone_ID == 333210 & Rates == 25  ~ "P Strip",
    Zone_ID == 333210 & Rates == 50  ~ "P Strip",
    Zone_ID == 333210 & Rates == 75  ~ "P Strip",
    
    Zone_ID == 333211 & Rates == 0  ~ "N Strip",
    Zone_ID == 333211 & Rates == 60  ~ "N Strip",
    Zone_ID == 333211 & Rates == 120  ~ "N Strip",
    
    Zone_ID == 333210 & Rates == 0  ~ "N Strip",
    Zone_ID == 333210 & Rates == 60  ~ "N Strip",
    Zone_ID == 333210 & Rates == 120  ~ "N Strip",
    
    
    #Nelson_3
    Zone_ID == 333311 & Rates == 0 & Yld < 1.5 ~ "P Strip",
    Zone_ID == 333311 & Rates == 25 & Yld > 1.5 ~ "P Strip",
    Zone_ID == 333311 & Rates == 50 & Yld < 1.5 ~ "P Strip",
    Zone_ID == 333311 & Rates == 75  ~ "P Strip",
    
    Zone_ID == 333310 & Rates == 0 & Yld > 1.8 ~ "P Strip",
    Zone_ID == 333310 & Rates == 25 & Yld < 1.7 ~ "P Strip",
    Zone_ID == 333310 & Rates == 50 & Yld > 1.7 ~ "P Strip",
    Zone_ID == 333310 & Rates == 75  ~ "P Strip",
    
    Zone_ID == 333311 & Rates == 0 & Yld < 1.5 ~ "N Strip",
    Zone_ID == 333311 & Rates == 25 & Yld > 1.5 ~ "N Strip",
    Zone_ID == 333311 & Rates == 50 & Yld < 1.5 ~ "N Strip",
    
    
    Zone_ID == 333311 & Rates == 0 & Yld > 1.5 ~ "N Strip",
    Zone_ID == 333311 & Rates == 25 & Yld < 1.5 ~ "N Strip",
    Zone_ID == 333311 & Rates == 50 & Yld > 1.5 ~ "N Strip",
    
    Zone_ID == 333310 & Rates == 0 & Yld < 1.8 ~ "N Strip",
    Zone_ID == 333310 & Rates == 25 & Yld > 1.7 ~ "N Strip",
    Zone_ID == 333310 & Rates == 50 & Yld < 1.7 ~ "N Strip",
    
    TRUE ~ Strip_Type
  ))

# is  paddock is missing code "Landmark	James_Falvey_2	Tim_McClelland_4	Mervyns" but I am not sure it should be included??
names(t.test_2019)
t.test_2019 <- t.test_2019 %>% 
  dplyr::mutate(Zone_ID = case_when(
    Paddock_tested == "Mervyns" ~ 312431,
    TRUE ~ as.double(Zone_ID)
  ) )




## I want to join details_2019 to t.test 

str(t.test_2019)
str(details_2019)

t.test_2019 <- t.test_2019 %>% 
  dplyr::mutate(for_join = paste0(Paddock_ID, Strip_Type, Rates))
details_2019 <- details_2019 %>% 
  dplyr::mutate(for_join = paste0(Paddock_ID, Strip_Type, Rate))

t.test2019_details <- full_join(details_2019, t.test_2019)
names(t.test2019_details)

# I have two problem paddocks Jeff (53621) no rates no analysis and Mervyns non zone 312431 

t.test2019_details <- t.test2019_details %>% 
  filter(Paddock_tested != "Mervyns")
t.test2019_details <- t.test2019_details %>% 
  filter(Paddock_ID != 53621)

t.test2019_details <- t.test2019_details %>%
  dplyr::select(Zone_ID,
                Paddock_ID,
                Strip_Type,
                Rate,
                GSP,
                Strip_Type,
                Total_sum_N_content,
                Total_sum_P_content,
                Yld,
                Organisation,
                Contact,
                Farmer,
                Paddock_tested,
                rainfall_class,
                AGROECOLOG,
                P_value,
                Mean_diff,
                rounded,
                Significant)
####################################################################################################################################################
## bring in rec rates ##

recom_rateDB2019 <- read_excel( "W:/value_soil_testing_prj/data_base/downloaded_sep2021/GRDC 2019 Paddock Database_SA_VIC_June11 2021.xlsx")
str(recom_rateDB2019)
# select only a few clms with recommedation 
recom_rateDB2019 <- recom_rateDB2019 %>% 
  dplyr::select(Zone_ID =    `Paddock code` ,
                Total_N = `Total N`, 
                p_rec =           `P rec`,
                n_rec_yld_low =   `N Rec (< 3 t/ha)` ,       
                n_rec_yld_med =   `N Rec (3-5 t/ha)` ,             
                n_rec_yld_high =  `N Rec (> 5 t/ha)`,
                Colwell,
                DGT,
                PBI
                
  ) 

recom_rateDB2019$n_rec_yld_low <- as.double(recom_rateDB2019$n_rec_yld_low)
recom_rateDB2019$n_rec_yld_med <- as.double(recom_rateDB2019$n_rec_yld_med)
recom_rateDB2019$n_rec_yld_high <- as.double(recom_rateDB2019$n_rec_yld_high)
recom_rateDB2019$Colwell <- as.double(recom_rateDB2019$Colwell)
recom_rateDB2019$DGT <- as.double(recom_rateDB2019$DGT)
recom_rateDB2019$PBI <- as.double(recom_rateDB2019$PBI)

recom_rateDB2019 <-  dplyr::mutate(recom_rateDB2019,  maxN = apply(recom_rateDB2019[4:6], 1, max, na.rm = TRUE))


# remove redunant clm and replace inf
recom_rateDB2019 <- recom_rateDB2019 %>% 
  mutate(
    maxN = case_when(
      maxN >= 0 ~ maxN,
      TRUE ~ NA_real_
    )
  )

recom_rateDB2019 <- recom_rateDB2019 %>% 
  dplyr::select(Zone_ID  ,
                p_rec ,
                maxN,
                Total_N,
                Colwell,
                DGT,
                PBI)

##make a paddock_ID clm
recom_rateDB2019$length_zoneID <- nchar(recom_rateDB2019$Zone_ID)
recom_rateDB2019 <- recom_rateDB2019 %>% 
  mutate(Paddock_ID =   
           case_when(length_zoneID == 6 ~ substr(Zone_ID, start = 1, stop = 5),
                     length_zoneID == 7 ~ substr(Zone_ID, start = 1, stop = 6)))
recom_rateDB2019$Paddock_ID <- as.double(recom_rateDB2019$Paddock_ID)



rm(details_2019, t.test_2019)

### join the t.test data to the recom rates
str(recom_rateDB2019)
str(t.test2019_details)

t.test_details_rec_rates <- left_join(t.test2019_details, recom_rateDB2019)
rm(recom_rateDB2019, t.test2019_details)
#############################################################################################################
### Redo the rec rates for N with my rainfall zone

t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(Rec_N_jax = case_when(
    rainfall_class == "low" & Total_N <= 80 ~ ((80 -Total_N)/0.5),
    rainfall_class == "medium" & Total_N <= 160 ~ ((160 -Total_N)/0.5),
    rainfall_class == "high" & Total_N <= 240 ~ ((240 -Total_N)/0.5),
    TRUE                           ~ 0  ))

str(t.test_details_rec_rates)

t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(critical_colwell = 4.6*( PBI^ (0.393)))
## is colwell greater than critical colwell?
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(colwell_thershold = case_when(
    Colwell > critical_colwell ~ "adequate",
    Colwell < critical_colwell ~ "p_required")  )

## if p is required how much extra colwell p is needed to get to critical thershold?
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(to_reach_col_thershold = case_when(
    colwell_thershold == "p_required" ~ critical_colwell - Colwell))

## what is the recomm P rate?
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(p_rec_jax = case_when(
    colwell_thershold == "p_required" ~ ((0.0019*PBI+2.146)*to_reach_col_thershold),
    colwell_thershold == "adequate" ~ 5
    ))
## clean up extra clms

names(t.test_details_rec_rates)

t.test_details_rec_rates <- t.test_details_rec_rates %>%
  dplyr::select(-"length_zoneID",
                - critical_colwell,
                - colwell_thershold,
                - to_reach_col_thershold)


###################################################################################################################################

```

The next step is getting the yield and GM and plot.
what is the yeild differnce between the approx rec rate and GSP for N and P and the 2 years

```{r stuff around GM respose for 2019 paddocks vs GSP, message=TRUE, warning=FALSE, include=FALSE}
#t.test_details_rec_rates <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/for_econmics/t.test_details_rec_rates_2019.csv")

str(t.test_details_rec_rates)


### difference between p rec and p applied

t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(diff_p_rec_applied = abs(Total_sum_P_content- p_rec_jax))
closest_match_p <-t.test_details_rec_rates %>%
  group_by(Zone_ID) %>% 
  summarise(closest_match_p = min(diff_p_rec_applied))


#Add this back in

t.test_details_rec_rates <- left_join(t.test_details_rec_rates, closest_match_p)
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(rec_rate_approx_p =
           case_when(
             closest_match_p == diff_p_rec_applied ~ "approx_rec_rate"))

unique(t.test_details_rec_rates$GSP)
t.test_details_rec_rates$GSP <- as.character(t.test_details_rec_rates$GSP)

str(t.test_details_rec_rates$GSP)

t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(GSP_Rec_both_p = case_when(
    GSP == "GSP"  & rec_rate_approx_p == "approx_rec_rate" ~ "both",
    is.na(GSP)            & rec_rate_approx_p == "approx_rec_rate" ~ "rec_rate",
    GSP == "GSP"  & is.na(rec_rate_approx_p) ~ "GSP",
    TRUE ~ "other"
  ))


### difference between N rec and N applied
names(t.test_details_rec_rates)

t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(diff_n_rec_applied = abs(Total_sum_N_content- Rec_N_jax))

closest_match_n <-t.test_details_rec_rates %>%
  group_by(Zone_ID) %>% 
  summarise(closest_match_n = min(diff_n_rec_applied))


#Add this back in


t.test_details_rec_rates <- left_join(t.test_details_rec_rates, closest_match_n)
str(t.test_details_rec_rates)
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(rec_rate_approx_n =
           case_when(
             closest_match_n == diff_n_rec_applied ~ "approx_rec_rate"))



t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  mutate(GSP_Rec_both_n = case_when(
    GSP == "GSP"  & rec_rate_approx_n == "approx_rec_rate" ~ "both",
    is.na(GSP)            & rec_rate_approx_n == "approx_rec_rate" ~ "rec_rate",
    GSP == "GSP"  & is.na(rec_rate_approx_n) ~ "GSP",
    TRUE ~ "other"
  ))








#### arrange the data so that I have the order of detail that reflects it.
names(t.test_details_rec_rates)
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  dplyr::select(

#Tier 1
Paddock_ID,
Strip_Type,
Organisation,
Contact,
Farmer,
Paddock_tested,
rainfall_class,
AGROECOLOG,

#Tier 2
Zone_ID,
Total_N,
Colwell,
DGT,
PBI,
p_rec,
maxN,
Rec_N_jax,
p_rec_jax,
 
#Tier 3
Rate,
GSP,
Total_sum_N_content,
Total_sum_P_content,
Yld,
P_value,
Mean_diff,
rounded,
Significant,

#Tier 3 details# 
diff_p_rec_applied,
closest_match_p,
rec_rate_approx_p,
GSP_Rec_both_p,
diff_n_rec_applied,
closest_match_n,
rec_rate_approx_n,
GSP_Rec_both_n
)    



##############################################################################
### add some GM to yld results 
##############################################################################
# convert the yield to income of grain $/ha
# this assumes that all yield is in t /ha 
# all crops are wheat
# the 5 year wheat average is $286 and is same for all sites.
names(df)
t.test_details_rec_rates <- t.test_details_rec_rates %>% mutate(grain_income = Yld * 286)

##############################################################################
## cost for test $3 per ha for rates the approx rate here some GSP are also approx rec rate labelled as both

names(t.test_details_rec_rates)
unique(t.test_details_rec_rates$GSP_Rec_both_p)
unique(t.test_details_rec_rates$GSP_Rec_both_n)

t.test_details_rec_rates <- t.test_details_rec_rates %>% mutate(cost_test = case_when(
  GSP_Rec_both_p == "rec_rate" ~ 3.00,
  GSP_Rec_both_p == "both" ~ 3.00,
  
  GSP_Rec_both_n == "rec_rate" ~ 3.00,
  GSP_Rec_both_n == "both" ~ 3.00,
  TRUE ~ 0.00))

## cost fert is based on rainfall class - define the rainfall class

t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  dplyr::mutate(
    variable_costs = case_when(
      Strip_Type == "P Strip" & rainfall_class == "low" ~     194,
      Strip_Type == "P Strip" & rainfall_class == "medium" ~  358,
      Strip_Type == "P Strip" & rainfall_class == "high" ~    540,
      
      Strip_Type == "N Strip" & rainfall_class == "low" ~     220,
      Strip_Type == "N Strip" & rainfall_class == "medium" ~  340,
      Strip_Type == "N Strip" & rainfall_class == "high" ~    498))

### I don't get this step but it converts N applied from kg/ha to cost of N $ha
str(t.test_details_rec_rates)
t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  dplyr::mutate(
    Cost_P_N_dollar_ha  = case_when(
      Strip_Type == "P Strip"  ~     Total_sum_P_content * 2.9,
      Strip_Type == "N Strip"  ~     Total_sum_N_content * 1.1))     

## GM
#GM = Income grain  cost test  variable cost  cost of N


t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  dplyr::mutate(
    total_cost = cost_test + variable_costs + Cost_P_N_dollar_ha,
    GM  = grain_income - total_cost)

names(t.test_details_rec_rates)
all_step_t.test_details_rec_rates <- t.test_details_rec_rates
neat_t.test_details_rec_rates <- t.test_details_rec_rates %>% 
  dplyr::select(-diff_p_rec_applied,
                -diff_n_rec_applied,
                -closest_match_p,
                -closest_match_n,
                -grain_income,
                -cost_test,
                -variable_costs,
                -Cost_P_N_dollar_ha,
                -total_cost  )

#write.csv(neat_t.test_details_rec_rates, "W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/for_econmics/GM_t.test_details_rec_rates2019.csv")





```